### 2019-04-15 paper/paper.tex
added correlation table

@@

\begin{figure}
  \includegraphics[width=0.5\textwidth]{figures/geo_mean_highest_pagerank.pdf}
  \caption{\code{npm} rank (PageRank) of the five packages with the lowest overall geometric mean}
  \label{topFive}
\end{figure}

@@

\begin{figure*}
  \includegraphics[width=1\textwidth]{figures/highest_ranked.pdf}
  \caption{\code{npm} rank (PageRank) of the five packages each year with the lowest geometric}
  \label{ranksByYear}
\end{figure*}

While these packages represent the most consistently popular
members of \code{npm}, we also evaluate the most popular packages
on a yearly basis. Figure \ref{ranksByYear} presents the top five packages
for each individual year from 2011 to 2019. As noted in the original paper,
the top packages per year are relatively stable from 2013 onwards \cite{Wittern:2016}.
One notable exception to this rule is the 2016 rise in popularity of \code{eslint},
a tool for improving the quality of \code{JavaScript} code\footnote{https://www.npmjs.com/package/eslint}.

@@

\begin{table}
  \centering
  % TODO NOTE THAT THIS HAS LOWER NUMBERS THAN THE ORIGINAL PAPER DUE TO MONTHLY PAGERANKS
  \begin{tabular}{c|c|c|c}
    Year & Top 10 & Top 100 & Top 250 \\
    \hline
    2010 & 13 & 103 & 253\\
    2011 & 25 & 297 & 701\\
    2012 & 6 & 46 & 136\\
    2013 & 3 & 38 & 114\\
    2014 & 1 & 40 & 96\\
    2015 & 4 & 38 & 86\\
    2016 & 4 & 29 & 62\\
    2017 & 0 & 12 & 48\\
    2018 & 0 & 15 & 31\\
    2019 & 0 & 4 & 12\\
  \end{tabular}
  \caption{Number of packages entering top \code{npm} ranks for the first time}
  \label{numEnteringTop}
\end{table}

>>>>

\begin{table}
  \centering
  % TODO NOTE THAT THIS HAS LOWER NUMBERS THAN THE ORIGINAL PAPER DUE TO MONTHLY PAGERANKS
  \begin{tabular}{c|c c c}
     & \code{npm} PageRank & Downloads & \code{GitHub} \\
    \hline
    \code{npm} PageRank & - & 0.389 & 0.405\\
    Downloads & 0.389 & - & 0.576\\
    \code{GitHub} & 0.405 & 0.576 & -\\

  \end{tabular}
  \caption{Spearman rank correlation coefficients between selected measures of popularity.}
  \label{corr}
\end{table}

@@

\begin{figure}
  \includegraphics[width=0.5\textwidth]{figures/geo_mean_highest_pagerank.pdf}
  \caption{\code{npm} rank (PageRank) of the five packages with the lowest overall geometric mean.}
  \label{topFive}
\end{figure}

@@

\begin{figure*}
  \includegraphics[width=1\textwidth]{figures/highest_ranked.pdf}
  \caption{\code{npm} rank (PageRank) of the five packages each year with the lowest geometric mean.}
  \label{ranksByYear}
\end{figure*}

While these packages represent the most consistently popular
members of \code{npm}, we also evaluate the most popular packages
on a yearly basis. Figure \ref{ranksByYear} presents the top five packages
for each individual year from 2011 to 2019. As noted in the original paper,
the top packages per year are relatively stable from 2013 onward \cite{Wittern:2016}.
One notable exception to this rule is the 2016 rise in popularity of \code{eslint},
a tool for improving the quality of \code{JavaScript} code\footnote{https://www.npmjs.com/package/eslint}.

@@

\begin{table}
  \centering
  % TODO NOTE THAT THIS HAS LOWER NUMBERS THAN THE ORIGINAL PAPER DUE TO MONTHLY PAGERANKS
  \begin{tabular}{c|c|c|c}
    Year & Top 10 & Top 100 & Top 250 \\
    \hline
    2010 & 13 & 103 & 253\\
    2011 & 25 & 297 & 701\\
    2012 & 6 & 46 & 136\\
    2013 & 3 & 38 & 114\\
    2014 & 1 & 40 & 96\\
    2015 & 4 & 38 & 86\\
    2016 & 4 & 29 & 62\\
    2017 & 0 & 12 & 48\\
    2018 & 0 & 15 & 31\\
    2019 & 0 & 4 & 12\\
  \end{tabular}
  \caption{Number of packages entering top \code{npm} ranks for the first time.}
  \label{numEnteringTop}
\end{table}
